% Verified against docs/findings.md and experiment-log.md on 2026-04-17.
\begingroup
\scriptsize
\setlength{\tabcolsep}{4pt}
\begin{tabularx}{\textwidth}{c l l l c c X}
\toprule
\# & Method & Category & Expected & Actual IDF1 & $\Delta$ & Hypothesis for Failure \\
\midrule
1 & CSLS distance & Association & Reduce hubness & 42.8\% & -34.7pp & Penalized genuine vehicle-type hubs and destroyed useful neighborhood structure. \\
2 & SAM2 foreground masking & Feature & Remove background noise & 68.8\% & -8.7pp & Removed contextual cues and clipped vehicle boundaries that still carry identity signal. \\
3 & Augoverhaul + CircleLoss model & Training & Better ReID features & 72.2\% & -5.3pp & Stronger augmentations and/or CircleLoss suppressed cues needed for cross-camera matching. \\
4 & \texttt{mtmc\_only=true} & Post-proc & Drop single-camera noise & 73.4\% & -5.0pp & Removed valid single-camera trajectories that still contribute positively to the final metric. \\
5 & AFLink motion linking (gap=100) & Association & Motion-based merges & 73.3\% & -3.8pp & Motion consistency is unreliable across non-overlapping cameras; false merges dominate. \\
6 & Global optimal tracker (person) & Tracking & Better assignment & 91.2\% & -3.5pp & Sliding-window assignment lost Kalman motion prediction and increased switches. \\
7 & CID\_BIAS camera-pair matrix & Association & Camera calibration & 75.1\% & -3.3pp & Single-model features were too brittle for camera-pair priors; bias matrix overfit sparse evidence. \\
8 & Tracker max\_gap=80 & Tracking & Longer track persistence & 75.0\% & -3.0pp & Overly long persistence increased false continuation and identity contamination. \\
9 & 384px ViT deployment & Feature & Higher resolution detail & 75.6\% & -2.8pp & Higher resolution emphasized viewpoint-specific textures that do not transfer across cameras. \\
10 & Denoise preprocessing & Feature & Cleaner crops & 75.7\% & -2.7pp & Denoising removed subtle appearance cues and altered feature statistics unfavorably. \\
11 & FAC feature augmentation & Association & KNN consensus & 75.0\% & -2.5pp & Cross-camera KNN consensus overwrote discriminative details with noisy neighbors. \\
12 & DMT camera-aware training & Training & Camera invariance & 75.8\% & -1.4pp & Improved validation mAP but over-specialized to camera cues rather than robust cross-camera identity. \\
13 & Feature concatenation (vs. score fusion) & Fusion & Richer representation & 76.8\% & -1.6pp & Mixed uncalibrated feature spaces and degraded similarity calibration. \\
14 & Hierarchical clustering & Association & Better global merges & 72.3--76.5\% & -1.0 to -5.1pp & Centroid averaging and dendrogram merges lost identity-specific signal and amplified early mistakes. \\
15 & max\_iou\_distance=0.5 & Tracking & Tighter matching & 76.8\% & -1.6pp & Over-tight association fragmented tracks instead of preventing harmful merges. \\
16 & PCA 512D & Feature & More dimensions & 77.5\% & -0.78pp & Extra dimensions preserved more noise than discriminative identity information. \\
17 & Network flow solver & Association & Reduce conflation & 76.9\% & -0.24pp & Slight metric gains elsewhere did not offset higher conflation than conflict-free CC. \\
18 & Score-level ensemble with weak secondary & Fusion & Model diversity & 77.4\% & -0.1pp & The 52.77\% mAP secondary model added noise rather than complementary signal. \\
19 & Reranking (k-reciprocal) & Association & Re-score similarities & --- & --- & Reciprocal neighbor sets contained false positives with the current feature quality; the experiment log records the direction of the effect but not a stable paired point estimate. \\
\bottomrule
\end{tabularx}

\vspace{0.4em}
\par\noindent\footnotesize Training-path dead ends such as CircleLoss ablations, VeRi-776 transfer, extended ResNet fine-tuning, and EMA are kept here because they directly support the paper's central claim that feature-space changes, not more association tuning, dominate the remaining MTMC gap.
\endgroup